Millions of Type Errors

### 2023-03-24 oopsla23/paper.tex
Spellcheck

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \anon{Roblox Studio} is a tool which places programming in the hands of
  millions of creators, ranging from high school students to professional
  development studios. It has the ability to report telemetry data,
  which allows large-scale measurement of the creator experience. In
  this paper, we discuss one use of telemtry, to measure the experience
  of type error reporting.
\end{abstract}

@@

As discussed in~\anon[(ANONYMIZED CITATION)]{\cite{bfj-hatra-2021}},
the goals of the \anon{Luau} type system are rather different from
a traditional type system, which focuses on compilation and memory safety.
\anon{Luau} has a very heterogenous user community, ranging from
students in code camps to professional development studios. These
creators have quite different needs, with different emphases on
enabling rapid creation and ensuring software quality.

@@

\anon{Roblox Studio} has a telemetry system, which is used to guage
the effectiveness of creation features. This system stochastically
determines which sessions should report telemety, and for those
sessions, reports telemetry records back with a summary of the
session. In the case of this study, the telemetry includes data on the
number of errors at various levels of granularity: in the current edit
region, in the current file, and in every file which was type
checked.

@@

Most users of \anon{Roblox Studio} do not opt in to type error
reporting, and so they do not see the ``squiggly underlining'' that
indicates a type error site. Nonetheless, the type inference system
still runs (since it drives automplete and other type-based tools) and
so we can record which type errors would have been reported had the
user enabled type error reporting. As a result, we can investigate
which type errors are  fixed by users, even if they did not opt in to
type error reporting.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \anon{Roblox Studio} is a tool which places programming in the hands of
  millions of creators, ranging from high school students to professional
  development studios. It has the ability to report telemetry data,
  which allows large-scale measurement of the creator experience. In
  this paper, we discuss one use of telemetry, to measure the experience
  of type error reporting.
\end{abstract}

@@

As discussed in~\anon[(ANONYMIZED CITATION)]{\cite{bfj-hatra-2021}},
the goals of the \anon{Luau} type system are rather different from
a traditional type system, which focuses on compilation and memory safety.
\anon{Luau} has a very heterogeneous user community, ranging from
students in code camps to professional development studios. These
creators have quite different needs, with different emphases on
enabling rapid creation and ensuring software quality.

@@

\anon{Roblox Studio} has a telemetry system, which is used to gauge
the effectiveness of creation features. This system stochastically
determines which sessions should report telemetry, and for those
sessions, reports telemetry records back with a summary of the
session. In the case of this study, the telemetry includes data on the
number of errors at various levels of granularity: in the current edit
region, in the current file, and in every file which was type
checked.

@@

Most users of \anon{Roblox Studio} do not opt in to type error
reporting, and so they do not see the ``squiggly underlining'' that
indicates a type error site. Nonetheless, the type inference system
still runs (since it drives autocomplete and other type-based tools) and
so we can record which type errors would have been reported had the
user enabled type error reporting. As a result, we can investigate
which type errors are  fixed by users, even if they did not opt in to
type error reporting.
